Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-21 rates-neurips-21/rates.tex
minor

Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
Roughly speaking, a surrogate regret bound takes the form
\begin{equation}
  \label{eq:surrogate-regret-bound-informal}
  \forall \text{ surrogate hypotheses } h, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,\qquad
\end{equation}
where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
For example, if we have a sequence of surrogate hypothesis $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can guarante an overall slow rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.

As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear, the overall rate would have been a fast $O(1/n)$.
\raft{Maybe a good place to cite the IEEE rates paper}
While much is known about surrogate regret bounds for important classes of losses, like proper losses\raf{Bob, others} and margin losses\raf{refs}, general results spanning very broad classes of loss functions are sparse.
Lacking such results, authors instead often prove bounds for specific losses from scratch, e.g. \raf{abstain}.

>>>>

Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
The idea is that we have ample results to quantify the rate at which surrogate regret approaches zero, and if we could bound the target regret in terms of the surrogate regret, we would arrive at an overall generalization rate.
Roughly speaking, a surrogate regret bound takes the form
\begin{equation}
  \label{eq:surrogate-regret-bound-informal}
  \forall \text{ surrogate hypotheses } h, \quad \Reg_\ell(\psi\circ h) \leq \zeta(\, \Reg_L(h) \,)~,\qquad
\end{equation}
where the \emph{regret transfer function} $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
For example, if we have a sequence of surrogate hypothesis $h_n$ achieving a fast rate $\Reg_L(h_n) = O(1/n)$, and $\zeta(\epsilon) = \sqrt{\epsilon}$, then we can guarante an overall slow rate of $\Reg_\ell(\psi \circ h_n) = O(1/\sqrt{n})$.

As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
\raft{Maybe a good place to cite the IEEE rates paper}
While much is known about surrogate regret bounds for important classes of losses, like proper losses\raf{Bob, others} and margin losses\raf{refs}, general results spanning very broad classes of loss functions are sparse.
Lacking such results, authors instead often prove bounds for specific losses from scratch, e.g. \raf{abstain}.
